<span style='line-height:60px; font-size:80px'>Catching competitors</span><font size=12>:</font><br><font size=8><span style='line-height:60px'>lexical evolution in diachronic corpora</span></font>

### 2019-08-19 news.Rmd
ruse2019

- Presenting a talk on lexical competition at the [CL2019](http://www.cl2019.org/). Slides with interactive plots [here](https://andreskarjus.github.io/cl2019talk.html). Also teaching a dataviz [workshop](https://andreskarjus.github.io/artofthefigure/cl2019).

>>>>

- Presenting a talk at the [RUSE 2019](http://rusesymposium.org.uk/), the Symposium on Representations, Usage and Social Embedding in Language Change (a slightly updated version of the CL2019 talk). Slides [here](https://andreskarjus.github.io/ruse2019).

- Presented a talk on lexical competition at the [CL2019](http://www.cl2019.org/). Slides with interactive plots [here](https://andreskarjus.github.io/cl2019talk.html). Also teaching a dataviz [workshop](https://andreskarjus.github.io/artofthefigure/cl2019).
